Distance Sampling in \proglang{R}

### 2015-12-06 paper.Rmd
add Jon and Lorenzo thanks
add STB, DLB and TAM to acknowledgements
reference to history in the JAE paper

For many years distance sampling analyses have been available via the Windows program Distance (or "DISTANCE"); for clarity henceforth "Distance for Windows" @Thomas:2010cf). From version 5 of Distance for Windows, R packages have been included to perform particular analyses (CITE Distance user manual). This paper shows how to fit detection functions, perform model checking and selection and estimate abundance in \proglang{R} using the package \pkg{Distance}. \pkg{Distance} is a wrapper package around the more complex (and more powerful) \pkg{mrds} and offers a subset of the analyses possible with that package.

@@

The authors would like to thank the many users of \pkg{Distance}, \pkg{mrds} and DISTANCE who have contributed bug reports and suggestions for improvements over the years.

>>>>

For many years distance sampling analyses have been available via the Windows program Distance (or "DISTANCE"); for clarity henceforth "Distance for Windows"). From version 5 of Distance for Windows, R packages have been included to perform particular analyses [@Thomas:2010cf, further details of the history of Distance for Windows are included in that paper]. This paper shows how to fit detection functions, perform model checking and selection and estimate abundance in \proglang{R} using the package \pkg{Distance}. \pkg{Distance} is a wrapper package around the more complex (and more powerful) \pkg{mrds} and offers a subset of the analyses possible with that package.

@@

The authors would like to thank the many users of \pkg{Distance}, \pkg{mrds} and DISTANCE who have contributed bug reports and suggestions for improvements over the years. We would particularly like to thank Steve Buckland, David Borchers, Tiago Marques, Jon Bishop and Lorenzo Milazzo for their contributions.
